The Importance of Affective States in Privacy Calculus

### 2021-04-30 submission.tex
references included

Privacy literacy does not necessarily translate into privacy conscious behavior — the great privacy paradox. To describe this seemingly irrational decision-making process, many studies have explored different models of this privacy calculus \cite{Kehr2015}\cite{Jian2013}. These privacy-infringing decisions despite purported privacy concerns may result in negative affective states such as guilt and shame. \\

>>>>

Privacy literacy does not necessarily translate into privacy conscious behavior — the great privacy paradox. To describe this seemingly irrational decision-making process, many studies have explored different models of this privacy calculus \cite{Kehr2015} \cite{Jian2013}. These privacy-infringing decisions despite purported privacy concerns may result in negative affective states such as guilt and shame. \\
